Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-08 paper/galsize_paper.tex
Updated figures and simplified orphan treatment

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/baseline_sham.pdf}
\caption{
{\bf Abundance matching clustering predictions.}
Using the abundance matching methods described in \S\ref{subsec:sham}, we compare the projected clustering of mock vs. SDSS galaxies. Each panel shows the comparison for a volume-limited sample defined by a different $\mstar-$threshold. Black points with error bars show SDSS measurements; solid black curves show the abundance matching prediction of our fiducial model, which includes the effect of orphan subhalos (see Appendix A). Including orphans mitigates the discrepancy in the clustering predicted by traditional, $\mpeak-$based SHAM based, though mild tension remains for $\mstar\gtrsim10^{10.75}\msun.$
}
\label{fig:baseline_sham_clustering}
\end{figure}
%-----------------------------------------------------------------------------------------------------

@@

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=12cm]{FIGS/rvir_only_wp_large_small_absolute.pdf}
\caption{
{\bf $\rhalf-$dependence of galaxy clustering.}
Red and blue points with error bars show our SDSS measurements of the clustering of small and large galaxies, respectively. For each volume-limited sample of $\mstar-$complete galaxies, the small and large subsamples have identical stellar mass functions, as shown in Figure \ref{fig:sizedefinition}. Small galaxies cluster much more strongly relative to large galaxies of the same stellar mass. Solid curves show the clustering predictions of the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}. The $\rvir-$based model inherits the shortcoming of ordinary abundance matching at $\mstar\gtrsim10^{10.75}\msun,$ although the model faithfully captures the {\em relative} clustering of small vs. large galaxies, as shown in Figure \ref{fig:clustering_ratio_upshot}.
}
\label{fig:rvir_only_clustering_absolute}
\end{figure*}
%-----------------------------------------------------------------------------------------------------

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=12cm]{FIGS/rvir_only_wp_ratios.pdf}
\caption{
{\bf $\rhalf-$dependence of galaxy clustering: clustering ratios.}
Closely related to Figure \ref{fig:rvir_only_clustering_absolute}, the y-axes show {\em clustering strength ratios,} defined as $(w_{\rm p}^{\rm large} - w_{\rm p}^{\rm small})/w_{\rm p}^{\rm all}.$ Thus a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass. Solid curves show the clustering ratio predictions of the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}. Normalizing the measurements and predictions by $w_{\rm p}^{\rm all}$ scales away the shortcoming of ordinary abundance matching at high stellar mass (see Figure \ref{fig:baseline_sham_clustering}), highlighting the successful prediction of the $\rvir-$based model for the $\rhalf-$dependence of galaxy clustering.
}
\label{fig:clustering_ratio_upshot}
\end{figure*}
%-----------------------------------------------------------------------------------------------------

@@

Since a rigorous calibration of $\mathcal{F}_{\rm orphan}$ is beyond the scope of the present work, we instead opt for a simple parameterization that yields reasonably accurate recovery of the galaxy clustering signal observed in SDSS. We model $\mathcal{F}_{\rm orphan}=\mathcal{F}_{\rm orphan}(M_{\rm peak},M_{\rm host}),$ where $\mpeak$ is the peak mass of the disrupted subhalo, and $\mhost$ is the present-day virial mass of its $z=0$ host halo. For the $\mpeak-$dependence, we select $50\%$ of disrupted subhalos with $\mpeak=10^{11}\msun,$ $0\%$ of subhalos with $\mpeak=10^{13}\msun,$ linearly interpolating in $\log\mpeak$ for intermediate values of $\mpeak.$ At each $\mpeak,$ the selection of disrupted halos is not random; instead, we preferentially select the subhalos with larger $\mhost,$ which we intend to offset the increased difficulty of subhalo-finding algorithms to identify subhalos with especially small values of  $\mu\equiv\mpeak/\mhost.$ We refer to this model as our ``fiducial orphan model". We assess the role of the nontrivial features in $\mathcal{F}_{\rm orphan}$ by randomly selecting the same number of orphan subhalos, referring to this alternate model as the ``random orphan model".

Figure \ref{fig:orphan_effects} illustrates the impact of the orphan selection function on $\mstar-$threshold clustering (top panel) and the satellite fraction (bottom panel). Comparing the black to the red curves shows that including orphans substantially boosts small-scale clustering due to the increased satellite fraction. Comparing the orange to the black curves, we see that randomly selecting orphans results in excessive small-scale clustering for the higher-mass threshold samples due to the inclusion of too many disrupted subhalos with large values of $\mpeak.$

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/baseline_sham_orphans.pdf}
\includegraphics[width=8cm]{FIGS/orphan_satellite_fraction.pdf}
\caption{
{\bf Impact of the orphan selection function.} The {\em top panel} is identical to Figure \ref{fig:baseline_sham_clustering}, but includes additional curves for the case of randomly selected orphan halos (orange curves), and no orphans at all (red curves). As a function of stellar mass, the {\em bottom panel} shows the satellite fraction, i.e., the fraction of objects that are not central galaxies.
}
\label{fig:orphan_effects}
\end{figure}
%-----------------------------------------------------------------------------------------------------

>>>>

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/baseline_sham.pdf}
\caption{
{\bf Abundance matching clustering predictions.}
Using the abundance matching methods described in \S\ref{subsec:sham}, we compare the projected clustering of mock vs. SDSS galaxies. Each panel shows the comparison for a volume-limited sample defined by a different $\mstar-$threshold. Black points with error bars show SDSS measurements; solid black curves show the abundance matching prediction of our fiducial model, which includes the effect of orphan subhalos (see Appendix A). Including orphans mitigates the discrepancy in the clustering predicted by traditional, $\mpeak-$based SHAM based, though mild tension remains on small scales for $\mstar\gtrsim10^{10.75}\msun,$ and on all scales for the $\mstar\gtrsim10^{9.75}\msun.$
}
\label{fig:baseline_sham_clustering}
\end{figure}
%-----------------------------------------------------------------------------------------------------

@@

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=12cm]{FIGS/rvir_only_wp_large_small_absolute.pdf}
\caption{
{\bf $\rhalf-$dependence of galaxy clustering.}
Red and blue points with error bars show our SDSS measurements of the clustering of small and large galaxies, respectively. For each volume-limited sample of $\mstar-$complete galaxies, the small and large subsamples have identical stellar mass functions, as shown in Figure \ref{fig:sizedefinition}. Small galaxies cluster much more strongly relative to large galaxies of the same stellar mass. Solid curves show the clustering predictions of the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}. The $\rvir-$based model inherits the shortcoming of ordinary abundance matching shown in Figure \ref{fig:baseline_sham_clustering}, although the model faithfully captures the {\em relative} clustering of small vs. large galaxies, as shown in Figure \ref{fig:clustering_ratio_upshot}.
}
\label{fig:rvir_only_clustering_absolute}
\end{figure*}
%-----------------------------------------------------------------------------------------------------

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=12cm]{FIGS/rvir_only_wp_ratios.pdf}
\caption{
{\bf $\rhalf-$dependence of galaxy clustering: clustering ratios.}
Closely related to Figure \ref{fig:rvir_only_clustering_absolute}, the y-axes show {\em clustering strength ratios,} defined as $(w_{\rm p}^{\rm large} - w_{\rm p}^{\rm small})/w_{\rm p}^{\rm all}.$ Thus a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass. Solid curves show the clustering ratio predictions of the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}. Normalizing the measurements and predictions by $w_{\rm p}^{\rm all}$ scales away the shortcoming of ordinary abundance matching (see Figure \ref{fig:baseline_sham_clustering}), highlighting the successful prediction of the $\rvir-$based model for the $\rhalf-$dependence of galaxy clustering.
}
\label{fig:clustering_ratio_upshot}
\end{figure*}
%-----------------------------------------------------------------------------------------------------

@@

In this appendix, we show two different a priori reasonable choices for the orphan selection function. Since a rigorous calibration of $\mathcal{F}_{\rm orphan}$ is beyond the scope of the present work, we instead opt for a simple parameterization that yields reasonably accurate recovery of the galaxy clustering signal observed in SDSS.

In both treatments studied here, we first throw out orphan subhalos with $V_{\rm max}/V_{\rm peak}<0.1,$ so that the most drastically disrupted subhalos remain unused. For our fiducial model used throughout the main body of the text, $\mathcal{F}_{\rm orphan}$ is defined by simply randomly select half of the orphan subhalos. For the alternative orphan selection function labeled as $M_{\rm host}-$dependent orphans in this appendix, we proceed as follows. We model $\mathcal{F}_{\rm orphan}=\mathcal{F}_{\rm orphan}(M_{\rm peak},M_{\rm host}),$ where $\mpeak$ is the peak mass of the disrupted subhalo, and $\mhost$ is the present-day virial mass of its $z=0$ host halo. For the $\mpeak-$dependence, we select $50\%$ of disrupted subhalos with $\mpeak=10^{11}\msun,$ $0\%$ of subhalos with $\mpeak=10^{13}\msun,$ linearly interpolating in $\log\mpeak$ for intermediate values of $\mpeak.$ At each $\mpeak,$ the selection of disrupted halos is not random; instead, we preferentially select the subhalos with larger $\mhost,$ which we intend to offset the increased difficulty of subhalo-finding algorithms to identify subhalos with especially small values of  $\mu\equiv\mpeak/\mhost.$

Figure \ref{fig:orphan_effects} illustrates the impact of the orphan selection function on $\mstar-$threshold clustering (top panel) and the satellite fraction (bottom panel). Comparing the black to the red curves shows that including orphans substantially boosts small-scale clustering due to the increased satellite fraction. Comparing the orange to the black curves, we see that random orphan selection, vs. the $M_{\rm host}-$dependent selection, results in similar clustering, with slight differences on the smallest scales at the highest masses. Because we have not been systematic in the calibration of $\mathcal{F}_{\rm orphan},$ we adopt the simpler, random orphan selection as the fiducial model shown in the main body of the text.

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/baseline_sham_orphans.pdf}
\includegraphics[width=8cm]{FIGS/orphan_satellite_fraction.pdf}
\caption{
{\bf Impact of the orphan selection function.} The {\em top panel} is identical to Figure \ref{fig:baseline_sham_clustering}, but includes additional curves for the case of $M_{\rm host}-$dependent orphan selection (orange curves), and no orphans at all (red curves). As a function of stellar mass, the {\em bottom panel} shows the satellite fraction, i.e., the fraction of objects that are not central galaxies.
}
\label{fig:orphan_effects}
\end{figure}
%-----------------------------------------------------------------------------------------------------
